---
title: "Nick Strayer"
output:
  html_document:
    css: styles.css
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(RColorBrewer)
library(htmltools)

htmltools::tagList(rmarkdown::html_dependency_font_awesome())

collabs <- read_tsv('https://raw.githubusercontent.com/nstrayer/network3d/customTooltips/data/ca-GrQc.txt', skip = 4, col_names = c('source', 'target'))

size <- 500
vertices <- data_frame(id = unique(collabs$source)) %>%
    mutate(
      index = 1:n(),
      color = sample(brewer.pal(9, 'RdYlBu'), size = n(), replace = TRUE),
      name = as.character(index),
      tooltip = paste0(
        '<h2>', index, '</h2>',
        '<p> Here are some random numbers ', rnorm(n()), '</p>'
      )
    ) %>%
    head(size)

  edges <- collabs %>%
    filter((source %in% vertices$id) & (target %in% vertices$id))

data <- list(
    edges = edges,
    vertices = vertices
  ) %>% jsonlite::toJSON()

```



```{r headerPlot, fig.align = 'center'}
r2d3::r2d3(
  data=data, 
  container = 'canvas', 
  script="network.js",
  width = '100%')
```


## About

<p>
I have been extremely lucky to work in many different realms, including as a <a href="http://www.nytimes.com/interactive/2016/08/26/us/college-student-migration.html">Journalist at the New York Times</a>, 
data scientist at the <a href="http://jhudatascience.org/"> Johns Hopkins Data Science Lab</a> and <a href="http://www.dealer.com/">Dealer.com</a> in Vermont,
"data artist in residence" at tech startup <a href="https://www.conduce.com/">Conduce</a> in California. 
Currently, I am a PhD candidate in biostatistics at Vanderbilt University where my research focuses on deep learning with medical data.                  
Recently (May '15), I graduated from the University of Vermont where I majored in
<strong>mathematics</strong> and
<strong>statistics</strong> and minored in
<strong>computer science.</strong>
</p>

<p>I like data. Manipulating it, modeling it, making it (simulation), visualizing it and yes, even cleaning
it. I do these things with some combination of <strong>R</strong>, <strong>Python</strong> and <strong>Javascript</strong>  
(d3.js in particular). Most recently I have been fascinated with conveying complex statistical topics
and methods using <a href="http://nickstrayer.me/binomialFun/confidenceIntervals">intuitive</a> and
<a href="http://nickstrayer.me/likelihood">interactive</a> <a href="http://nickstrayer.me/binomialFun/">graphics.</a> </p>
<p>My current research interests include:
<strong>visualizing latent spaces in deep learning</strong>,
<strong>data/model visualization</strong> and
<strong>scientific communication</strong>.

If you want to read about me and my pursuits in a more eloquently written form, I was recently <a href="http://www.uvm.edu/newsstories/news/deeper_story_data">profiled</a>                    by my alma mater.
</p>
<p>
When I am not in "school mode" I love to bike places, read science fiction and wander around gardens/musuems.
</p>


<p>Have a fantastic day!</p>


## Projects


For a much more up-to-date and topical list of my work, check out the data science/statisics/visualization blog that I run with [Lucy D'Agostino McGowan](https://www.lucymcgowan.com/): [Live Free or Dichotomize](http://livefreeordichotomize.com/). 
```{r}
projects_data <- jsonlite::fromJSON('projects.json')
```

```{r}
github_icon <- HTML("<i class='fa fa-github fa-lg' style='padding-right:5px' aria-hidden='true'></i>")
link_icon <- HTML("<i class='fa fa-home fa-lg' style='padding-left:5px' aria-hidden='true'></i>")

point_icon <- HTML("<span style='vertical-align: text-bottom;'><i class='fa fa-circle' aria-hidden='true' style='font-size: 5px;'></i></span>")

html_dom = list()
for(i in 1:nrow(projects_data)){
  project = projects_data[i,]
  
  html_dom[[i]] <- div(
    h3( a(project$title, href = project$link) ),
    div(class = 'photo_and_description',
      img(src = project$photo),
      div(
        class = 'description', 
        purrr::map(
          project$descriptions[[1]], 
          ~list(point_icon, span(HTML(.)), br())
        ), 
        p(
          a(HTML(github_icon), href = project$github),
          a(HTML(link_icon), href = project$link),
          align = 'center'
        )
      ) 
    ),
    hr()
  )
}
div(html_dom, class = 'project_list')
```




## CV

<div id="resumeButton" class="col-sm-12 col-md-10 col-md-offset-1">
<h4 id="buttonText">Expand C.V.</h4>
</div>

<div id="resumeDiv" class="col-sm-12 col-md-10 col-md-offset-1">
<iframe src="http://docs.google.com/gview?url=https://www.dropbox.com/s/ixzkmp69nskohtb/Strayer_CV.pdf?dl=1&embedded=true"
style="width:100%; height:700px;" frameborder="0"></iframe>
</div>

```{js}
function open_hide_cv(){
  let link = $('#buttonText');
  $('#resumeDiv').slideToggle('slow', function() {
    if ($(this).is(':visible')) {
      link.text('Close');
    } else {
      link.text('Expand C.V.');
    }
  });
}
$('#resumeButton').click(open_hide_cv);
open_hide_cv();
```


## Contact

I am always interested in getting involved in new projects or just connecting with others. Feel free
to get in touch!

**email:** n.strayer (at) vanderbilt (dot) edu


**twitter:** <a href="https://twitter.com/NicholasStrayer" target="_blank">NicholasStrayer </a>
   

**github:** <a href="https://github.com/nstrayer" target="_blank">nstrayer </a>
