---
title: "Nick Strayer"
output:
  html_document:
    css: styles.css
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(magrittr)
library(htmltools)
library(magrittr)

image <- png::readPNG('images/website_header.png') %>% 
  extract(,,1)

width <- ncol(image)
height <- nrow(image)

image_tidy <- image %>% 
  as_tibble() %>% 
  set_colnames(1:width) %>% 
  mutate(y = 1:height) %>% 
  gather(x, value, -y) %>% 
  filter(value == 0) %>% 
  transmute(
    x = as.integer(x)/width,
    y = y/height,
    dist_from_center = (x - 0.5)^2 + (y - 0.5)^2
  ) %>% 
  arrange(dist_from_center) %>% 
  select(-dist_from_center)

num_points <- nrow(image_tidy)

num_lines <- 25
num_x_points <- ceiling(num_points/num_lines)

x <- seq(0,1,length.out = num_x_points)

get_beta <- function(shape1, shape2){
  tibble(
    x = x, 
    y = dbeta(x,shape1 = shape1, shape2 = shape2),
    class = glue::glue('{shape1},{shape2}')
  )
}
beta_data <- expand.grid(
  shape1 = 2,
  shape2 = seq(1.5, 10, length.out = num_lines)
) %$% 
  purrr::map2_df(shape1, shape2, get_beta) %>% 
  head(num_points) %>% 
  mutate(y = -y/max(y) + 1)

# ggplot(beta_data, aes(x = x, y = y, color = class)) +
#   geom_line() +
#   guides(color = FALSE)

htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```



```{r headerPlot}
r2d3::r2d3(
  data = list(text = image_tidy,beta = beta_data), 
  dependencies = c('javascript/regl.min.js', "javascript/helpers.js"), 
  container = 'div', 
  width = "100%",
  script = "javascript/particles.js")
```


## About


I have been extremely lucky to work in many different realms, including as a [Journalist at the New York Times](http://www.nytimes.com/interactive/2016/08/26/us/college-student-migration.html), data scientist at the [Johns Hopkins Data Science Lab](http://jhudatascience.org/) and [Dealer.com](http://www.dealer.com/) in Vermont, and "data artist in residence" at startup [Conduce](https://www.conduce.com/) in California. 

Currently, I am a PhD candidate in biostatistics at Vanderbilt University. I received my undergraduate degree from the University of Vermont where I majored in __mathematics__ and __statistics__ and minored in __computer science.__

My research focuses on __unsupervized and semi-supervized methods__ for exploring large omics datasets, with a heavy focus on __visualization__. 

I like data. Manipulating it, modeling it, making it (simulation), visualizing it and yes, even cleaning it. I do these things with some combination of __R__, __Python__, and __Javascript__ (d3.js in particular). Most recently I have been fascinated with conveying complex statistical topics and methods using [intuitive](http://nickstrayer.me/binomialFun/confidenceIntervals) and [interactive](http://nickstrayer.me/likelihood) [graphics.](http://nickstrayer.me/binomialFun/)

If you want to read about me and my pursuits in a more eloquently written form, I was recently [profiled](https://www.uvm.edu/uvmnews/news/deeper-story-data) by my alma mater.

When I am not in "school mode" I love to bike places, read science fiction, take photos, and wander around gardens/musuems.


Have a fantastic day!


## Projects


For a much more up-to-date and topical list of my work, check out the data science/statisics/visualization blog that I run with [Lucy D'Agostino McGowan](https://www.lucymcgowan.com/): [Live Free or Dichotomize](http://livefreeordichotomize.com/). 
```{r}
projects_data <- jsonlite::fromJSON('projects.json')
```

```{r}
github_icon <- HTML("<i class='fa fa-github fa-lg' style='padding-right:5px' aria-hidden='true'></i>")
link_icon <- HTML("<i class='fa fa-home fa-lg' style='padding-left:5px' aria-hidden='true'></i>")

point_icon <- HTML("<span style='vertical-align: text-bottom;'><i class='fa fa-circle' aria-hidden='true' style='font-size: 5px;'></i></span>")

html_dom = list()
for (i in 1:nrow(projects_data)) {
  project = projects_data[i,]
  
  has_github <- !is.na(project$github)
  
  if (has_github) {
    links <- p(
      a(HTML(github_icon), href = project$github),
      a(HTML(link_icon), href = project$link),
      align = 'center'
    )
  } else {
    links <- p(
      a(HTML(link_icon), href = project$link),
      align = 'center'
    )
  }
  
  html_dom[[i]] <- div(
    h3( a(project$title, href = project$link) ),
    div(class = 'photo_and_description',
      img(src = project$photo),
      div(
        class = 'description', 
        purrr::map(
          project$descriptions[[1]], 
          ~list(point_icon, span(HTML(.)), br())
        ), 
        links
      ) 
    ),
    hr()
  )
}
div(html_dom, class = 'project_list')
```




## CV

<div id="resumeButton" class="col-sm-12 col-md-10 col-md-offset-1" style="margin-left:0; width: 100%;">
<h4 id="buttonText">Expand C.V.</h4>
</div>

<div id="resumeDiv" class="col-sm-12 col-md-10 col-md-offset-1">
<iframe src="http://docs.google.com/gview?url=https://github.com/nstrayer/cv/raw/master/strayer_cv.pdf&embedded=true" style="width:100%; height:700px;" frameborder="0"></iframe>
</div>

<br>

View HTML version of CV with links [here](nickstrayer.me/cv).


```{js}
function open_hide_cv(){
  let link = $('#buttonText');
  $('#resumeDiv').slideToggle('slow', function() {
    if ($(this).is(':visible')) {
      link.text('Close');
    } else {
      link.text('Expand C.V.');
    }
  });
}
$('#resumeButton').click(open_hide_cv);
open_hide_cv();
```


## Contact

I am always interested in getting involved in new projects or just connecting with others. Feel free
to get in touch!

**email:** n.strayer (at) vanderbilt (dot) edu


**twitter:** <a href="https://twitter.com/NicholasStrayer" target="_blank">NicholasStrayer </a>
   

**github:** <a href="https://github.com/nstrayer" target="_blank">nstrayer </a>
